---
title: "GW Assignment - Biden Transition"
author: "YOUR NAME HERE"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(janitor)
library(scales)
library(gt)
library(kableExtra)
options(dplyr.summarise.inform = FALSE)

#run the script for step 03 to update the datasets to capture the current live verions
#and load all the new dataset objects into the environment (you'll see them populate on the upper right window)
source("03_compare_current_with_previous.R")


```

**Note: use either kable/kableExtra or gt tables to format your final tables for the questions below. You'll likely find it easier to figure out the data parts first, then once that's done add the table formatting.**

# AGENCY TEAMS

Come up with the necessary R code to return the following for the agency review teams.

### *New Names*

Below write code to show the new names added to the agency review team lists since the prior data provided.  
  

```{r, echo=FALSE}
#retrieving data from most updated webscrape
transition_data_current <- readRDS("processed_data/transition_data_scraped.rds")
transition_data_current

#retrieving data from previous webscrape
transition_data_previous <- readRDS("archived_data/transition_data_archived_2020_11_24t09_52.rds")
transition_data_previous

#building table that lists new names
updated_names <- anti_join(transition_data_current, transition_data_previous, by = "idstring")
updated_names_important<-updated_names %>% 
  select(agency,
         name,
         most_recent_employment,
         source_of_funding)

updated_names_important_tbl<-updated_names_important %>% 
  knitr::kable(
    caption="New Team Members",
    col.name=c("Agency", "Name", "Most Recent Employment", "Source of Funding"),
  ) %>% 
  kableExtra::kable_material_dark(c("striped", "hover"))
 
updated_names_important_tbl

```


### *Aggregate Team Changes*

Add data to show the total number of people appointed to each agency team, along with change since last time reflecting the number of new people added. Omit agencies with no change at all.  
  

```{r, echo=FALSE}
#finding number of positions from updated data
agencycount_current <- transition_data_current %>% 
  count(agency, name = "current_count")
agencycount_current

#finding number of positions from previous data
agencycount_previous <- transition_data_previous %>% 
  count(agency, name = "previous_count")
agencycount_previous

#joining datasets
agencycount_compare <- left_join(agencycount_current, agencycount_previous, by = "agency")
agencycount_compare

#adding change column
agencycount_compare <- agencycount_compare %>% 
  mutate(
    change = current_count - previous_count
  )

#ommitting agencies with no change
agencycount_compare<-agencycount_compare %>% 
  filter(change!=0) %>% 
  select(agency,
         change)


agencycount_compare_tbl<-agencycount_compare %>% 
  knitr::kable(
    caption="Change in Team Members",
    col.name=c("Agency", "# of New Members"),
  ) %>% 
  kableExtra::kable_material_dark(c("striped", "hover"))

agencycount_compare_tbl
 


```


### *Largest and Smallest Overall*

Show the top 10 **largest** agency review teams as of today:

```{r, echo=FALSE}
#Using slice function 
top_10_agencies<-agencycount_current %>% 
  arrange(desc(current_count)) %>% 
  slice(1:10)

top_10_agencies_tbl<-top_10_agencies %>% 
   knitr::kable(
    caption="Top 10 Agencies by Amount of Members",
    col.name=c("Agency", "Current Count"),
  ) %>% 
  kableExtra::kable_material_dark(c("striped", "hover"))

top_10_agencies_tbl





```

Show the top **smallest** agency review teams as of today - which we'll define here as less than five members:

```{r, echo=FALSE}
smallest_agencies<-agencycount_current %>% 
  filter(current_count<5) %>% 
  arrange(desc(current_count))

smallest_agencies_tbl<-smallest_agencies %>% 
   knitr::kable(
    caption="Smallest Agencies by Amount of Members",
    col.name=c("Agency", "Current Count"),
  ) %>% 
  kableExtra::kable_material_dark(c("striped", "hover"))

smallest_agencies_tbl




 

```



# WHITE HOUSE SENIOR STAFF

Come up with the necessary R code to return the following for the WH senior staff.

### *New Names*

Below write code to show the new names added to the senior staff lists since the prior data provided.  
  

```{r, echo=FALSE}

#Creating the scrape function
scrape_names_staff <- function(namenum) {
  #set url for nominees list page
  url <- "https://buildbackbetter.gov/the-administration/white-house-senior-staff/"
  #perform the GET call
  website1 <- GET(url)
  
  #grab the names
  names <- html_nodes(content(website1), "h3")
  #isolate just one
  name1 <- print(html_text(names, trim = TRUE)[[namenum]])
  
  #grab the titles
  titles <- html_nodes(content(website1), "span.acctext--con")
  #show just one
  title1 <- print(html_text(titles, trim = TRUE)[[namenum]])
  
  #grab the links
  links <- html_nodes(content(website1), "a.full-link")
  #show just one
  link1 <- html_attr(links, 'href')[[namenum]]
  
  #combine into dataframe
  df <- data.frame("name" = name1, "title" = title1, "link" = link1)
  
  return(df)
  
}

scrape_names_staff(1)

#Loop through all the names on the site.
myurl2 <- "https://buildbackbetter.gov/the-administration/white-house-senior-staff/"
website2 <- GET(myurl2) 
names2 <- html_nodes(content(website2), "h3")
num_names_staff <- length(html_text(names2, trim = TRUE))
num_names_staff <- seq(1, num_names_staff)
num_names_staff
staff_data_scraped <- map_df(num_names_staff, scrape_names_staff)
staff_data_scraped <- staff_data_scraped %>% 
  mutate(
    idstring = str_trim(paste0(name, title))
  ) %>% 
  as_tibble()

staff_data_scraped

#Save the data
saveRDS(staff_data_scraped, "processed_data/staff_data_scraped.rds")
write_xlsx(staff_data_scraped, "processed_data/staff_data_scraped.xlsx")

filestring <- paste0("archived_data/staff_data_archived_", Sys.time())
filestring <- str_replace_all(filestring, "-", "_")
filestring <- str_replace_all(filestring, ":", "_")
filestring <- str_replace(filestring, " ", "t")
filestring <- str_sub(filestring, 1, -4L)
filestring <- paste0(filestring, ".rds")
saveRDS(staff_data_scraped, filestring)

#Join the two datasets together to figure out which names are new.
current_senior_staff<-readRDS("processed_data/staff_data_scraped.rds")
previous_senior_staff<-readRDS("archived_data/staff_data_archived_2020_11_24t14_00.rds")


updated_senior_staff <- anti_join(current_senior_staff, previous_senior_staff, by = "idstring")
senior_staff_important<-updated_senior_staff %>% 
  select(name,
         title)

senior_staff_important

#Making more suitable chart
new_staff_tbl<-senior_staff_important %>% 
  knitr::kable(
    caption="New Senior Staff Members",
    col.name=c("Name", "Title"),
  ) %>% 
  kableExtra::kable_material_dark(c("striped", "hover"))

new_staff_tbl


 

```


### *Total Number of Current vs. Previous*

Add code to show the total number of people currently named to the WH senior staff, vs. the previous total number.  
  

```{r, echo=FALSE}







```
